Best Practices for Developing Monte Carlo Methodologies in Molecular Simulations [Article v\versionnumber]

### 2025-06-02 paper/paper.tex
last reviewer comment
figures png->pdf

\begin{figure}
\begin{centering}
\includegraphics[width=8.5cm]{../figures/detailed_balance.png}
\caption{
Probabilities for all possible transitions between two states, old and new, are illustrated.
Proposed configurations and other possible transitions are shown with black dashed circles and arrows, respectively.
Detailed balance is achieved when, for every pair of states, the probability to be in one of the states and then to accept a transition into another state is equal to the probability to be in that other state and then to accept the reverse transition.
}
\label{fig:detailed_balance}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/lhs_nvt.png}
\caption{
Detailed balance is violated if the tunable displacement parameter, $\delta$, decreases.
If the particle is displaced from the old position, $\mathbf{r}_o$, within $\delta_o$ in each dimension, then the particle may not be able to return to $\mathbf{r}_o$ in the reverse trial if the next displacement is within $\delta_n<\delta_o$.
This is why $\delta$ should change only during equilibration and not during production simulations.
}
\label{fig:lhs_nvt}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=8.5cm]{../figures/npt.png}
\caption{
Detailed balance is violated if the particle positions are not scaled with the volume and one of the particles is wrapped across periodic boundaries.
On the left, the top-most particle is wrapped to the bottom due to the decrease in volume when particle positions are not scaled.
The reverse move, a subsequent increase in volume without scaling, will not return the system to its original microstate, shown in the center.
On the right, detailed balance is obeyed when the particle positions are scaled with the volume.
}
\label{fig:npt}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=8.5cm]{../figures/muvt.png}
\caption{
Insertion trials randomly add a particle, here shown in blue, uniformly within the simulation volume.
Deletion trials remove a random particle, and are the reverse of insertions.
}
\label{fig:muvt}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=8.5cm]{../figures/sgcmc.png}
\caption{
Semi-$\mu VT$ change of a particle of type $i$, shown in red, into a particle of type $j$, shown in black.
The total number of particles remains constant.
}
\label{fig:sgcmc}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/gibbs_particle.png}
\caption{
Gibbs ensemble transfer of the particle shown in blue from periodic domain $1$ to periodic domain $2$, and the reverse trial.
The total number of particles remains constant.
}
\label{fig:gibbs_particle}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/gibbs_volume.png}
\caption{
Gibbs ensemble transfer of volume from periodic domain $1$ to periodic domain $2$, and the reverse trial.
The total volume remains constant and the particle positions are scaled as described in Section~\ref{sec:lhs_dv}.
}
\label{fig:gibbs_volume}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/muvt_cb.png}
\caption{
Multiple first bead configurational bias insertion and deletion considers randomly-generated positions for a newly inserted particle, shown by the dashed circles, in an existing fluid of particles, shown by the black circles.
The most favorable position has the highest Rosenbluth probability of selection, which is shown in blue due to excluded volume overlap of the other red positions with the existing fluid.
The deletion step does not consider other positions or particles for deletion, but to obey detailed balance, the Rosenbluth factor in the deletion step includes the existing position as well as other randomly-generated positions.
}
\label{fig:muvt_cb}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/cavity.png}
\caption{
Cavity bias insertion and deletion may utilize a collection of points, here shown by a grid of red and blue points, which are tested for cavities.
Cavities are where another particle could fit without excluded volume overlap with existing particles, shown here as black circles with grey excluded volumes.
The red circles with dashed lines are periodic images, and the blue dots in the center are the only points in the grid that a new particle could be added onto without overlap.
}
\label{fig:cavity}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/energybias.png}
\caption{
Energy bias insertion and deletion \cite{snurr_prediction_1993} divides the simulation domain into voxels, with $25$ shown here by the dashed lines.
One voxel, $v$, is chosen for the available insertion volume according to a probability Boltzmann-weighted by the energy of interaction with a rigid adsorbent frame, shown by the black circles.
The reverse move is when the newly inserted fluid particle, shown in blue, is randomly chosen for deletion among all the fluid particles.
}
\label{fig:energybias}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/muvt_target.png}
\caption{
Insertion and deletion trials in a targeted region, $v$.
Similar to Fig.~\ref{fig:energybias}, the targeted region could be carefully chosen to avoid excluded volume overlap with a rigid adsorbent framework.
}
\label{fig:muvt_target}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/avb.png}
\caption{
Insertion and deletion of a blue particle of type $i$ within the aggregation volume (AV), shown in green, of an existing particle of type $j$.
}
\label{fig:avb_gce}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/avb2.png}
\caption{
AVBMC2 displacement of a blue particle of type $i$ from outside to inside the AV, $v_{AV}$ shown in green, of an existing target particle of type $j$, and the reverse trial.
}
\label{fig:avbmc2}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/avb4.png}
\caption{
AVBMC4 displacement of a blue particle of type $m$ from inside the AV, $v_j$ of an existing target particle of type $j$, into the AV of an existing target particle $k$, $v_k$, and the reverse trial.
AVBMC3 does not allow overlapping AV as shown here \cite{chen_improving_2001}.
}
\label{fig:avbmc4}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=4.5cm]{../figures/dccb_draw.png}
\caption{
An illustration of the old and new Rosenbluth terms for hard circles as described in Fig.~\ref{fig:lhs_nvt}.
The red box shows the positions available to $\pi_{cn}$ while the blue box shows the positions available to $\pi_{co}$.
Although the entire free volume is available to $\pi_{cn}$, it is not all available to $\pi_{co}$.
Thus, $\pi_{cn} \neq \pi_{co}$.
}
\label{fig:dccb_draw}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/cluster.png}
\caption{
Detailed balance is violated if two separate clusters coalesce during a rigid cluster translation.
In the forward transition, the blue cluster is displaced near a separate cluster shown in red.
If this move were allowed, the reverse cluster move would be impossible because clusters are moved rigidly and cannot be broken apart during the trial.
To obey detailed balance, reject rigid cluster moves that result in the coalescence of two originally separate clusters.
}
\label{fig:cluster}
\end{centering}
\end{figure}

@@

MC often involves the perturbation of a subset of the system instead of the entire system.
Only the energy of interaction of the perturbed particles needs to be computed to obtain the change in the energy of the system.
The energy of the system after a trial is accepted is the previous energy of the system plus the change.
This energy is referred to as the running total energy.
However, round off errors at the limit of numerical precision cause the running total energy to be different from the total energy calculated based on the interactions of all the particles.
This difference increases with the number of trials.
It is recommended to infrequently compute the energy of the entire system and compare the total energy with the running total energy from each energy change.
If the relative differences are not within an acceptable tolerance based on machine precision and the magnitude of the total energy, then this is a clear indication there is a problem with the way that the change in energy was computed, and an error or warning should be made visible.
If the relative difference is within an acceptable tolerance, the running total energy is then reset to the newly calculated value and the simulation continues.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=3cm]{../codes/random_orientation.png}
\caption{
Example output from Code Block~\ref{sim:random_orientation} shows $10^3$ uniformly random points on a sphere in blue, and $10^3$ points in orange randomly generated about the upwards $z$-axis using an orientational tunable parameter, $\delta=0.3$.
\label{fig:orientation_perturbation}
}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=3cm]{../codes/spherical_shell.png}
\caption{
Example output from Code Block~\ref{sim:spherical_shell} shows $10^5$ small blue points randomly generated inside a spherical shell of outer radius $3$ and inner radius $2$.
\label{fig:spherical_shell}
}
\end{centering}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=8.5cm]{../figures/detailed_balance.pdf}
\caption{
Probabilities for all possible transitions between two states, old and new, are illustrated.
Proposed configurations and other possible transitions are shown with black dashed circles and arrows, respectively.
Detailed balance is achieved when, for every pair of states, the probability to be in one of the states and then to accept a transition into another state is equal to the probability to be in that other state and then to accept the reverse transition.
}
\label{fig:detailed_balance}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/lhs_nvt.pdf}
\caption{
Detailed balance is violated if the tunable displacement parameter, $\delta$, decreases.
If the particle is displaced from the old position, $\mathbf{r}_o$, within $\delta_o$ in each dimension, then the particle may not be able to return to $\mathbf{r}_o$ in the reverse trial if the next displacement is within $\delta_n<\delta_o$.
This is why $\delta$ should change only during equilibration and not during production simulations.
}
\label{fig:lhs_nvt}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=8.5cm]{../figures/npt.pdf}
\caption{
Detailed balance is violated if the particle positions are not scaled with the volume and one of the particles is wrapped across periodic boundaries.
On the left, the top-most particle is wrapped to the bottom due to the decrease in volume when particle positions are not scaled.
The reverse move, a subsequent increase in volume without scaling, will not return the system to its original microstate, shown in the center.
On the right, detailed balance is obeyed when the particle positions are scaled with the volume.
}
\label{fig:npt}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=8.5cm]{../figures/muvt.pdf}
\caption{
Insertion trials randomly add a particle, here shown in blue, uniformly within the simulation volume.
Deletion trials remove a random particle, and are the reverse of insertions.
}
\label{fig:muvt}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=8.5cm]{../figures/sgcmc.pdf}
\caption{
Semi-$\mu VT$ change of a particle of type $i$, shown in red, into a particle of type $j$, shown in black.
The total number of particles remains constant.
}
\label{fig:sgcmc}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/gibbs_particle.pdf}
\caption{
Gibbs ensemble transfer of the particle shown in blue from periodic domain $1$ to periodic domain $2$, and the reverse trial.
The total number of particles remains constant.
}
\label{fig:gibbs_particle}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/gibbs_volume.pdf}
\caption{
Gibbs ensemble transfer of volume from periodic domain $1$ to periodic domain $2$, and the reverse trial.
The total volume remains constant and the particle positions are scaled as described in Section~\ref{sec:lhs_dv}.
}
\label{fig:gibbs_volume}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/muvt_cb.pdf}
\caption{
Multiple first bead configurational bias insertion and deletion considers randomly-generated positions for a newly inserted particle, shown by the dashed circles, in an existing fluid of particles, shown by the black circles.
The most favorable position has the highest Rosenbluth probability of selection, which is shown in blue due to excluded volume overlap of the other red positions with the existing fluid.
The deletion step does not consider other positions or particles for deletion, but to obey detailed balance, the Rosenbluth factor in the deletion step includes the existing position as well as other randomly-generated positions.
}
\label{fig:muvt_cb}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/cavity.pdf}
\caption{
Cavity bias insertion and deletion may utilize a collection of points, here shown by a grid of red and blue points, which are tested for cavities.
Cavities are where another particle could fit without excluded volume overlap with existing particles, shown here as black circles with grey excluded volumes.
The red circles with dashed lines are periodic images, and the blue dots in the center are the only points in the grid that a new particle could be added onto without overlap.
}
\label{fig:cavity}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/energybias.pdf}
\caption{
Energy bias insertion and deletion \cite{snurr_prediction_1993} divides the simulation domain into voxels, with $25$ shown here by the dashed lines.
One voxel, $v$, is chosen for the available insertion volume according to a probability Boltzmann-weighted by the energy of interaction with a rigid adsorbent frame, shown by the black circles.
The reverse move is when the newly inserted fluid particle, shown in blue, is randomly chosen for deletion among all the fluid particles.
}
\label{fig:energybias}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/muvt_target.pdf}
\caption{
Insertion and deletion trials in a targeted region, $v$.
Similar to Fig.~\ref{fig:energybias}, the targeted region could be carefully chosen to avoid excluded volume overlap with a rigid adsorbent framework.
}
\label{fig:muvt_target}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/avb.pdf}
\caption{
Insertion and deletion of a blue particle of type $i$ within the aggregation volume (AV), shown in green, of an existing particle of type $j$.
}
\label{fig:avb_gce}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/avb2.pdf}
\caption{
AVBMC2 displacement of a blue particle of type $i$ from outside to inside the AV, $v_{AV}$ shown in green, of an existing target particle of type $j$, and the reverse trial.
}
\label{fig:avbmc2}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/avb4.pdf}
\caption{
AVBMC4 displacement of a blue particle of type $m$ from inside the AV, $v_j$ of an existing target particle of type $j$, into the AV of an existing target particle $k$, $v_k$, and the reverse trial.
AVBMC3 does not allow overlapping AV as shown here \cite{chen_improving_2001}.
}
\label{fig:avbmc4}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=4.5cm]{../figures/dccb_draw.pdf}
\caption{
An illustration of the old and new Rosenbluth terms for hard circles as described in Fig.~\ref{fig:lhs_nvt}.
The red box shows the positions available to $\pi_{cn}$ while the blue box shows the positions available to $\pi_{co}$.
Although the entire free volume is available to $\pi_{cn}$, it is not all available to $\pi_{co}$.
Thus, $\pi_{cn} \neq \pi_{co}$.
}
\label{fig:dccb_draw}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/cluster.pdf}
\caption{
Detailed balance is violated if two separate clusters coalesce during a rigid cluster translation.
In the forward transition, the blue cluster is displaced near a separate cluster shown in red.
If this move were allowed, the reverse cluster move would be impossible because clusters are moved rigidly and cannot be broken apart during the trial.
To obey detailed balance, reject rigid cluster moves that result in the coalescence of two originally separate clusters.
}
\label{fig:cluster}
\end{centering}
\end{figure}

@@

MC often involves the perturbation of a subset of the system instead of the entire system.
Only the energy of interaction of the perturbed particles needs to be computed to obtain the change in the energy of the system.
The energy of the system after a trial is accepted is the previous energy of the system plus the change.
This energy is referred to as the running total energy.
However, round off errors at the limit of numerical precision cause the running total energy to be different from the total energy calculated based on the interactions of all the particles.
This difference increases with the number of trials.
It is recommended to infrequently compute the energy of the entire system and compare the total energy with the running total energy from each energy change.
The total energy may also be compared and updated during trials which update all the particles, such as volume changes.
If the relative differences are not within an acceptable tolerance based on machine precision and the magnitude of the total energy, then this is a clear indication there is a problem with the way that the change in energy was computed, and an error or warning should be made visible.
If the relative difference is within an acceptable tolerance, the running total energy is then reset to the newly calculated value and the simulation continues.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=3cm]{../figures/random_orientation.png}
\caption{
Example output from Code Block~\ref{sim:random_orientation} shows $10^3$ uniformly random points on a sphere in blue, and $10^3$ points in orange randomly generated about the upwards $z$-axis using an orientational tunable parameter, $\delta=0.3$.
\label{fig:orientation_perturbation}
}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=3cm]{../figures/spherical_shell.png}
\caption{
Example output from Code Block~\ref{sim:spherical_shell} shows $10^5$ small blue points randomly generated inside a spherical shell of outer radius $3$ and inner radius $2$.
\label{fig:spherical_shell}
}
\end{centering}
\end{figure}
